\documentclass[11pt]{article}
    \title{\textbf{User Story Example}}
    \author{Justal Kevin}
    \date{22 January 2020}
    
    \addtolength{\topmargin}{-3cm}
    \addtolength{\textheight}{3cm}
\begin{document}

\maketitle
\thispagestyle{empty}

\section{Preface}
The goal of this document is to give you an idea of what could be an user story well detailed for a very smooth implementation for the frontend and backend. At the end of the document, the reader should have no question because all of them are already answered in the document. For this example, I will take something that everybody know : messenger.\\

\section{Prerequisit}
I consider that the app has been install by the users.

\section{Goal}
The goal is to allow a logged user to send a message to another logged user.

\section{Personna}

There is only two kind of user possible. The logged user and the user not logged.

\section{Permissions}

\subsection{Permission of an user on his message}

WEF

\begin{table}[!htb]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		& Read & Write \\  [0.5ex]
		\hline 
		Logged user & Yes & Yes \\ 
		\hline 
		Not logged user & No & No \\ 
		\hline 
	\end{tabular} 
    \label{table:nonlin}
\end{table}

\subsection{Permission of an user on the message of someone else}

\begin{table}[!hbt]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		& Read & Write \\  [0.5ex]
		\hline 
		Logged user & Y & No \\ 
		\hline 
		Not logged user & No & No \\ 
		\hline 
	\end{tabular} 
	\label{table:nonlin}
\end{table}

\section{Contributing}
If you'd like to contribute to this project, here's some ideas:
\begin{description}
\addtolength{\itemindent}{0.80cm}
\itemsep0em 
\item[Development] fix bugs or add features to our C/GTK codebase
\item[Documentation] edit the user guide to improve user experience
\item[Localization] translate Gummi in your native language
\item[Testing] try out the latest and report your findings
\end{description}
Refer to the \emph{Getting Involved}\footnote{https://github.com/alexandervdm/gummi/wiki/Getting-Involved} section on our wiki for more information. 

\section{What's next}
Within the 0.8.x release series we will focus on adding minor features but mostly fixing bugs. New functionality will be integrated into the next major release. An overview of currently accepted features can be found on the 0.9.0 milestone\footnote{https://github.com/alexandervdm/gummi/milestone/3} page.

\section{In closing}
We hope you will enjoy using this release as much as we enjoyed creating it. If you have any further comments, suggestions or wish to report an issue, please visit \emph{\textbf{https://gummi.app}}. 

\end{document}

